Blaming the Typeless: \\ Scalable, Human-Centric Python Localization

### 2018-08-20 paper/main.tex
rephrase the motex a bit

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{pgfplots}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

@@

\begin{figure}
\begin{verbatim}
year = int(time.strftime("%Y"))
age = input("Enter your age")
print("You will be twice as old in:")
print(year + age)
\end{verbatim}
\caption{A buggy program}
\end{figure}

Consider the program in Fig. 1, adapted from our dataset. The program
attempts to use the current year and the user's age to compute their
birth year and the year they can vote. However, while line 1 correctly
turns the current year from a string into an int, this `int' call is
missing from line 2 so `age' remains a string, and thus the addition
on line 4 causes the program to crash.

Notice that while a correct fix (and the one that the programmer
actually used) is to add an `int' call to line 2, another possible ``fix''
would be to \textit{remove} the `int' call from line 1 - both year and
age would then be strings, and the addition on line 4 would be interpreted
as string concatenation. This shows the necessity of a heuristic, data-driven
approach, since without test cases there is no way to tell for sure which
fix is better.

We can also start to see some features which will be
important for finding bugs: we will need the \textit{type} of age, as
well as some \textit{contextual} information about how it's used in the program.

>>>>

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{listings}
\usepackage{myref}
\usepackage{pgfplots}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}

\newcommand\lt[1]{{\lstinline|#1|}}
\lstset{language=python}
\definecolor{dkgreen}{rgb}{0,0.5,0}
\definecolor{dkred}{rgb}{0.5,0,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\lstset{basicstyle=\ttfamily\bfseries\footnotesize,
  morekeywords={virtualinvoke},
  keywordstyle=\color{blue},
  ndkeywordstyle=\color{red},
  commentstyle=\color{dkred},
  stringstyle=\color{dkgreen},
  numbers=left,
  numberstyle=\ttfamily\footnotesize\color{gray},
  stepnumber=1,
  numbersep=10pt,
  backgroundcolor=\color{white},
  tabsize=4,
  showspaces=false,
  showstringspaces=false,
  xleftmargin=.23in
}

\begin{document}

@@

\begin{figure}
\begin{lstlisting}
year = int(time.strftime("%Y"))
age = input("Enter your age")
print("You will be twice as old in:")
print(year + age)
\end{lstlisting}
\caption{
\label{fig-motex} 
A program with multiple fault localizations (e.g.,
lines 1 and 2).} 
\end{figure}

Consider the program in \figref{motex}, adapted from our dataset of
human submissions. The program attempts to carry out some simple arithmetic
based on a given number and the current year. When executed, however, the
program raises an exception on line 4, related to the addition of an
integer variable to a string variable.

One reasonable fix (and the one that the programmer actually used in this
case) is to add \lt{int()} cast on line 2. However, another possible
``fix'' would be to \textit{remove} the \lt{int()} cast from line 1, in
which case both variables hold string values at runtime, and the addition
on line 4 would be interpreted as string concatenation. While the second
fix creates a well-typed program, it is less likely to correspond to
developer intent, and is thus less likely to be helpful as a debugging aid.

This simple example highlights a key fault localization challenge in such
dynamically-typed settings: a runtime type error alone may not contain
enough information to pinpoint the human-preferred localization from among
many valid-but-less-helpful localizations. Our insight is that the relevant
information is not in the types (e.g., string or integer) alone but in the
context in which the values are used.  We propose an approach based on
machine learning over a combination of static and dynamic contextual
features.
